\documentclass[12pt,a4paper]{article}
%\usepackage[margin=1.2in]{geometry}
\title{MOVA signature project: University Competition Application}
\author{Sebastien Duc}
\date{}

\begin{document}
    \maketitle

    \section{Overview}
    We consider an application where several universities are participating to a tournament.
    We can imagine that for the first round of the tournament, universities are organized into
    pairs. Let's consider one pair, and let's denote the two universities by $U_1$ and $U_2$. $U_1$ and $U_2$  are in competition.
    In this application, $U_1$ provides quizzes/challenges/riddles to students in $U_2$. Similarily $U_2$ provides quizzes to students in $U_1$.
    Students in a university are forming teams. We assume that teams have a certain amount of time (for example one week) to complete the current quiz/challenge/riddle. 
    Each team in a university have a different quiz\footnote{If several teams in a university have the same quiz, then they can copy on each other to increase the final score.}.
    When completed they send it to the server of both universities and get a score. At the end of the first round, all the best of the two universities 
    (i.e. the ones with the highest cumulated score of all teams in the university) in the pairs are 
    promoted to the second round. The game goes on the same way until round $n$ with only on pair (only two universities) and the best of the two wins the game.

    \section{Security}
    For this part let us consider one pair with universities $U_1$ and $U_2$ as before. Let us denote the server of $U_1$ by $S_1$ and the server of $U_2$ by $S_2$.
    We can assume that communication between $S_1$ and $S_2$ are confidential, autenticated and preserve integrity.
    When $U_1$ creates a quiz/challenge for students of $U_2$ they sign it with MOVA and then send it to them. In that way, the students are ensured that the quiz comes indeed
    from $U_1$ and that it is not a fake quiz from other cheating students who wants to make them lose time, hence lose score.
    Then, when the students are sending back the quiz to $S_2$, $S_2$ can sign the filled quiz with MOVA and send it to $S_1$. Finally $S_1$ receives the filled quiz and verify both signatures.
    For signatures coming from $S_2$, $S_1$ can run a batch verification with $S_2$

    \section{Problems}
    First we need to keep authentication and integrity between the students and their university server, because we don't want other malicious students to be able to modify the answer 
    of the quiz. This is not really an issue, we can assume that there is an infrastructure inside the university that allow students and the server to have a secure channel.
    We also have to assume that $S_2$ doesn't modify the results of the quizzes before signing them. Again this is not a real issue, because the server is supposed to be honest.

    \section{Using classical Signatures}
    In this application we could try to use classical signature. For the signature of the unfilled quiz (the signature signed by $S_1$, when $S_1$ is the quiz provider), 
    MOVA does not bring much compared to classical signatures, because
    \begin{itemize}
        \item It is not a problem that the signature is universally verifiable
        \item We don't need the signature to be invisible
        \item We cannot use batch verification
        \item It is not really usefull for the signatures to be very short
    \end{itemize}
    For the signature of the filled quiz (signed by $S_2$, when $S_1$ is the quiz provider), we exploit the fact that $S_1$
    runs batch verification. But the invisibility property of the signature is useless since communication between the two 
    server is confidential\footnote{Maybe even the signature added by $S_2$ is 
    useless since the channel is confidential.}.

    \section{Conclusion}
    MOVA signatures don't seem to bring much for this application and classical signatures would make things easier. And we need channels keeping confidentiality, authenticity and integrity
    between the two servers and between the students and the server of their university which should not be a problem in practice.




\end{document}
